### 2024-07-19 getting-started.qmd
20240718 - save big data files for use in other chapters
20240718 - load 4th down data
20240718 - callout note for 4th down data b/c it takes a long time to run

@@

nfl_4thdown <- nfl4th::load_4th_pbp(seasons = 2014:2023)
```

@@

@@

>>>>

load(file = here("data", "nfl_pbp.RData"))
```

@@

::: {#nte-download4thDownData .callout-note title="Downloading 4th down data"}
Note: the following code takes a while to run.
:::

```{r}
nfl_4thdown <- nfl4th::load_4th_pbp(seasons = 2014:2023)
```

@@

load(file = here("data", "nfl_4thdown.RData"))
```

@@

load(file = here("data", "nfl_participation.RData"))
```
